Active Learning from Blackbox to Timed Connectors

### 2016-04-20 shortpaper/paper.tex
.

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.45\textwidth]{./images/actl.pdf}
  \end{center}
  \caption{Active Automata Learning}
  \label{fig:activelearning}
\end{figure}

@@

The L* algorithm takes a set of input actions $\mathcal{I}$ and a oracle interface (which plays the
role of SUL) as its parameters. And it returns a so-called \emph{observation table} as the final
hypothesis. (Observation table is a widely-used data structure, which can represent a Mealy machine
by its external observation.)
In each iteration, the algorithm will:
\begin{enumerate}
  \item \emph{Enclose the hypothesis.} Active learning is very similar to a breadth-first-search
    process on an unknown Mealy machine. At first, only the initial state is visible to us. We then
    explore different input actions and check if they can lead to some state that is already known.
    If every edge targets to an explored state, we will say that the hypothesis is \emph{closed}.
  \item \emph{Equivalence checking.} After the hypothesis is enclosed, we need to check if the
    current hypothesis is equivalent to the real model. Such $eq$ operation returns a
    \emph{true} if they are equivalent, or a counter-example if not.
  \item \emph{Counter-example Analysis.} As mentioned before, we use suffixes to distinguish
    different states. Consequently, lack of proper suffix may lead to counter-examples. By the
    \emph{suffix} function, we can analyze the counter-example and find out which suffix is left out.
\end{enumerate}

@@

\section{Conclusion and Fu ture Work}
In this paper, we come up with an approach to extract timed connectors from blackbox
implementations. We propose \emph{parameterized Mealy machine} to describe the behavior of Reo
connectors. Then we define the product operator and link operator, which can be used to
construct complex connectors from simpler ones.
Besides, we show how PMMs behave as the bridge between Reo connectors and concrete Mealy
machines with timed action T provided.

>>>>

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.45\textwidth]{./images/actl.png}
  \end{center}
  \caption{Active Automata Learning}
  \label{fig:activelearning}
\end{figure}

@@

The L* algorithm takes a set of input actions $\mathcal{I}$ and a oracle interface (which plays the
role of SUL) as its parameters. And it returns a so-called \emph{observation table} as the final
hypothesis. (Observation table is a widely-used data structure, which can represent a Mealy machine
by its external observation.)
In each iteration, the algorithm will:
\begin{enumerate}
  \item \emph{Enclose the hypothesis.} Active learning is very similar to a breadth-first-search
    process on an unknown Mealy machine. At first, only the initial state is visible to us. We then
    explore different input actions, and check if their following state is already explored.
    If every edge targets to an explored state, we will say that the hypothesis is \emph{closed}.
  \item \emph{Equivalence checking.} With a closed hypothesis generated, we still need $eq$ to check
    if it is equivalent to the system-under-learn. \emph{Eq} returns \emph{true} if they are
    equivalent, or a counter-example if not.
  \item \emph{Counter-example Analysis.} As mentioned before, we use suffixes to distinguish
    different states. Consequently, the correctness of our hypothesis relies heavily on proper suffixes.
    The \emph{suffix} function are designed to analyze counter-examples and find out which suffix is
    left out.
\end{enumerate}

@@

\section{Conclusion and Future Work}
In this paper, we come up with an approach to extract timed connectors from blackbox
implementations. We propose \emph{parameterized Mealy machine} to describe the behavior of Reo
connectors. Then we define the product operator and link operator, which can be used to
construct complex connectors from simpler ones.
Besides, we show how PMMs behave as the bridge between Reo connectors and concrete Mealy
machines with timed action T provided.
